sims

### 2025-07-08 sims/sims.Rmd
adjust Figure 1

This file simulates the data used in Figures 1, 2, and 3 of the manuscript and then creates some plots.

@@

```{r}
p13.1 <-ggplot(lifetable_fig1, aes(x = bin, y = hazard,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits = c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
 # ggtitle("hazard and conditional accuracy functions") +
  xlab("time bin endpoint (ms)") +
  ylab("hazard") +
  theme(axis.text.x = element_text(angle = 90),
        panel.grid.minor.x = element_blank()) +
  annotate("label", x = 1.7, y = .95,
           label = "h(t) = P(RT = t | RT ≥ t)",
           fill = "white",           # White background
           color = "black", 
           size = 7, 
           hjust = 0)
p13.1

@@

```{r}
p13.2 <-ggplot(ca, aes(x = bin, y = ca,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits=c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("time bin endpoint (ms)") +
    ylab("conditional accuracy") +
   theme(axis.text.x = element_text(angle = 90),
         panel.grid.minor.x = element_blank()) +
   annotate("label", x = 1.5, y = .25,
           label = "ca(t) = P(correct | RT = t)",
           fill = "white",           # White background
           color = "black", 
           size = 7, 
           hjust = 0)

>>>>

This file simulates the data used in old Figures 1, 2, and 3 of the manuscript and then creates some plots.

Figure 1 of revision 1 can be found in section 13.

@@

```{r}
p13.1 <-ggplot(lifetable_fig1, aes(x = bin, y = hazard,
                         colour = condition, linetype=condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits = c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
 # ggtitle("hazard and conditional accuracy functions") +
  xlab("time bin t's endpoint (ms)") +
  ylab("hazard") +
  theme(axis.text.x = element_text(angle = 90),
        panel.grid.minor.x = element_blank()) +
  annotate("label", x = 1.7, y = .95,
           label = "h(t) = P(RT = t | RT ≥ t)",
           fill = "white",           # White background
           color = "black", 
           size = 7, 
           hjust = 0)
p13.1

@@

```{r}
p13.2 <-ggplot(ca, aes(x = bin, y = ca,
                         colour = condition, linetype=condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits=c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("time bin t's endpoint (ms)") +
    ylab("conditional accuracy") +
   theme(axis.text.x = element_text(angle = 90),
         panel.grid.minor.x = element_blank()) +
   annotate("label", x = 1.5, y = .25,
           label = "ca(t) = P(correct | RT = t)",
           fill = "white",           # White background
           color = "black", 
           size = 7, 
           hjust = 0)
